\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 cfhtlens.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.  This is even more unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}. \shahab{(not sure I entirely agree with this last sentence, please see email)}

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.    We argue that this artificial reduction in the error by a factor of $\sim 3$ could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.

>>>>

Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.    We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.

### 2016-12-05 conclusion.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

>>>>

The treatment of photo-$z$ uncertainties in \cite{kitching/etal:2016} is based on a simple linear shift of redshift distributions. This has been shown to be insufficient to capture the full complexity of the problem. More importantly though, it seems like \cite{kitching/etal:2016} apply the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong direction. Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, in agreement with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.

### 2016-12-05 theory.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

\subsection{The Flat-Sky approximation and Extended Limber Approximation}
The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{bartelmann/schneider:2001}, given by
\be
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\kappa(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\ee
where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
\be 
P^{ij}_\kappa(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
\label{eqn:Pkappa} 
\ee
Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.  The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.   \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ is given by
\be
T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} \, .
\label{eqn:Tl}
\ee
When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.  The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.  In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.

>>>>

\subsection{The Flat-Sky approximation and Extended Limber Approximation}
The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{bartelmann/schneider:2001}, given by
\be
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\ee
where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
\be 
P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
\label{eqn:Pkappa} 
\ee
Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.  The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.   \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
\be
T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} \, .
\label{eqn:Tl}
\ee
The corresponding pre-factor for the convergence power spectrum, along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum, is given in \citet{jk12}.

When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.  The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.  In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
